Asthma Cohort Descriptive Epidemiology

### 2017-12-07 r_scripts/analysis/asthma_cohort_descriptive_epi.Rmd
working on descriptives for asthma cohort

```{r setup, echo =F, warning=F, message=F}
library(tidyverse) # general data wrangle
library(survival) # conditional logistic regression

@@

>>>>

```{r setup, echo =F, warning=F, message=F}
library(tidyverse) # general data wrangle

# load outcomes vectors
load("./data/health/outcome_list.RData")
# subset asthma and saba vector
asthma_icd9 <- pluck(outcome_icd9_list, "asthma")
saba_ndc <- pluck(outcome_icd9_list, "saba")

@@

Read cohort dataset (reading in a small chunk for now.)

```{r cohort_import}
# read path
read_path <- "./data/health/2013-oregon_asthma_cohort.csv"
# read in asthma cohort (reading a million rows for now)
asthma_cohort <- data.table::fread(read_path, 
  # read options
  header = T, nrows = 10000, colClasses = rep("character", 72)) %>% 
  # replace *NULL* with NA
  mutate_all(funs(replace(., .== "*NULL*" | . == "", NA))) %>% 
  # create visit type indicator 
  mutate(visit_type = as.factor(
    case_when((dx1 %in% asthma_icd9) ~ "dx_asthma_primary",
    # asthma but not as a primary
    !(dx1 %in% asthma_icd9) & (dx2 %in% asthma_icd9 | dx3 %in% asthma_icd9 | 
      dx4 %in% asthma_icd9 | dx5 %in% asthma_icd9 | dx6 %in% asthma_icd9 | 
      dx7 %in% asthma_icd9 | dx8 %in% asthma_icd9 | dx9 %in% asthma_icd9 | 
      dx10 %in% asthma_icd9 | dx11 %in% asthma_icd9 | dx12 %in% asthma_icd9 | 
      dx13 %in% asthma_icd9) ~ "dx_asthma_not_primary",
    # other dx 
    !(dx1 %in% asthma_icd9 | dx2 %in% asthma_icd9 | dx3 %in% asthma_icd9 | 
      dx4 %in% asthma_icd9 | dx5 %in% asthma_icd9 | dx6 %in% asthma_icd9 | 
      dx7 %in% asthma_icd9 | dx8 %in% asthma_icd9 | dx9 %in% asthma_icd9 | 
      dx10 %in% asthma_icd9 | dx11 %in% asthma_icd9 | dx12 %in% asthma_icd9 | 
      dx13 %in% asthma_icd9) & is.na(ndc) ~ "dx_other",
    # ndc code
    (ndc %in% saba_ndc) ~ "pharm_saba",
    !is.na(ndc) & !(ndc %in% saba_ndc) ~ "pharm_other")))
```
